NMRlipids Databank: Overlay Databank of Lipid Membrane Simulations Arising from Open Collaboration

### 2022-08-09 main.tex
Update text

>>>>

For the permeation of water through membranes, the number of permeation events in each trajectory was first calculated using the code by Camilo et al.~\cite{camilo2022}, available at~\url{https://github.com/crobertocamilo/MD-permeation}. The permeation was then calculated from equation $P=r/2c_w$, where $r$ is the rate per time and area, and $c_w$ is the concentration of water in bulk with the value of 33.3679\,(nm)$^{-3}$~\cite{venable19}.
